Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-05-18 paper/letter.tex
rewriting results

\tol\ is a compact star forming dwarf galaxies (CDGs) that presents a
strong Ly-$\alpha$ emission \cite{Thuan97} with two features that had
so far evaded a natural physical interpratation.
First, it has symmetric profile  without any systemic displacement
from the expected line-center. 
Second, it shows a triple peak, while the most common observational
feature corresponds either to a single or asymetric double peak. 
We have attempted an interpretation of the Ly-$\alpha$ line in
\tol\ by including the effect of gas bulk rotation.
We find that this model provides a satisfactory explanation of \tol's
puzzling features.

Figure 1. summarizes our findings.
Dots represent the observational data for \tol with the
overplot from our best fit model from the full radiative transfer
simulation.   
The parameters for the best fit are
$v_{max}=300$\kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K.
The optical depth and temperature can be translated into a column
density of $\log N_{HI} / \mathrm{atoms\ cm}^{-2} =
  20.5$.   
Our model is also able to constrain the angle
between the rotation axis and the observational line-of-sight to $\theta=65^{\circ}\pm$.
To determine the uncertainties we perform a Markov Chain Monte
Carlo calculation using an approximate analytical solution for the
Ly-$\alpha$ spectrum including rotational effects.

>>>>

\tol\ is a compact star forming dwarf galaxy that presents a
strong Ly-$\alpha$ emission \cite{Thuan97} with two important
features. 
First, it has symmetric profile  without any systemic displacement
from the expected line-center. 
Second, it shows a triple peaked profile. 
Commonly, the Ly-$\alpha$ line features a single or asymetric double peak. 
These two special features in \tol\ had evaded a natural physical
interpratation so far.

We find that a rotating spherical gas distribution provides a
satisfactory explanation of \tol's puzzling features.  
Figure 1. summarizes our findings.
Dots represent the observational data for \tol with the
overplot from our best fit model from the full radiative transfer
simulation.   
The parameters for the best fit are a rotational velocity of
$v_{max}=300$\kms, an optical depth $\tau=1\times10^7$ and temperature
of $T=1.5\times 10^{4}$K.
The optical depth and temperature can be translated into a column
density of $\log N_{HI} / \mathrm{atoms\ cm}^{-2} =
  20.5$.   
Our model is also able to constrain the angle
between the rotation axis and the observational line-of-sight to
$\theta=65^{\circ}\pm$. 
To determine the uncertainties we perform a Markov Chain Monte
Carlo calculation using an approximate analytical solution for the
Ly-$\alpha$ spectrum including rotational effects.
